Generative Adversarial Networks

### 2017-12-08 cs6735/assignment/report.tex
almost done results!!

\subsection{Car Data}
\begin{itemize}[leftmargin=*]
  \item[] \bb{Title}: Car Evaluation Database
  \item[] \bb{Date}: June 1997
  \item[] \bb{Number of Samples}: 1728
  \item[] \bb{Number of Attributes}: 6
  \item[] \bb{Attribute Information}:
  \item[]
  \begin{tabular}{l c c c }
    \bb{Description} & \bb{Values}            & \bb{Type} \\
    buying           & v-high, high, med, low & Discrete  \\
    maint            & v-high, high, med, low & Discrete  \\
    doors            & 2, 3, 4, 5-more        & Discrete  \\
    persons          & 2, 4, more             & Discrete  \\
    lug\_boot        & small, med, big        & Discrete  \\
    safety           & low, med, high         & Discrete
  \end{tabular}
  \item[] \bb{Class Target}: Car Quality
  \item[] \bb{Class Information}:
  \item[]
  \begin{tabular}{l c c c c }
    \bb{Description} & \bb{Value} & \bb{Count} & \bb{Percentage} \\
    Unacceptable     & unacc      & 1210       & 70.023\%        \\
    Acceptable       & acc        & 384        & 22.222\%        \\
    Good             & good       & 69         & 3.993\%         \\
    Very Good        & v-good     & 65         & 3.762\%
  \end{tabular}
  \item[] \bb{Missing Attributes}: none
\end{itemize}

\subsection{E. Coli Data}
\begin{itemize}[leftmargin=*]
  \item[] \bb{Title}: Protein Localization Sites
  \item[] \bb{Date}: September 1997
  \item[] \bb{Number of Samples}: 336
  \item[] \bb{Number of Attributes}: 8
  \item[] \bb{Attribute Information}:
  \item[]
  \begin{tabular}{l c c c }
    \bb{Description} & \bb{Values}       & \bb{Type}  \\
    Sequence Name    &  Accession Number & Discrete   \\
    mcg              & 0.00 - 0.89       & Continuous \\
    gvh              & 0.16 - 1.00       & Continuous \\
    lip              & 0.48 - 1.00       & Discrete   \\
    chg              & 0.50 - 1.00       & Discrete   \\
    aac              & 0.00 - 0.88       & Continuous \\
    alm1             & 0.03 - 1.00       & Continuous \\
    alm2             & 0.00 - 0.99       & Continuous
  \end{tabular}
  \item[] \bb{Class Target}:  Localization Site
  \item[] \bb{Class Information}:
  \item[]
  \begin{tabular}{l c c c c }
    \bb{Description}           & \bb{Value} & \bb{Count} & \bb{Percentage} \\
    Cytoplasm                  & cp         & 143        & 42.56\%         \\
    Inner Membrane             & im         & 77         & 22.92\%         \\
    Perisplasm                 & pp         & 52         & 15.48\%         \\
    Inner Membrane Uncleavable & imU        & 35         & 10.42\%         \\
    Outer Membrane             & om         & 20         & 5.95\%          \\
    Outer Membrane             & omL        & 5          & 1.49\%          \\
    Inner Membrane Lipoprotein & imL        & 2          & 0.59\%          \\
    Inner Membrane Cleavable   & imS        & 2          & 0.59\%
  \end{tabular}
  \item[] \bb{Missing Attributes}: none
\end{itemize}

\subsection{Letter Recognition Data}
\begin{itemize}[leftmargin=*]
  \item[] \bb{Title}: Letter Image Recognition Data
  \item[] \bb{Date}: January 1991
  \item[] \bb{Number of Samples}: 20000
  \item[] \bb{Number of Attributes}: 16
  \item[] \bb{Attribute Information}:
  \item[]
  \begin{tabular}{l c c c }
    \bb{Description} & \bb{Values}            & \bb{Type}  \\
    x-box	           & 0 - 9                  & Continuous \\
    y-box	           & 0 - 9                  & Continuous \\
    width	           & 0 - 9                  & Continuous \\
    high 	           & 0 - 9                  & Continuous \\
    onpix	           & 0 - 9                  & Continuous \\
    x-bar	           & 0 - 9                  & Continuous \\
    y-bar	           & 0 - 9                  & Continuous \\
    x2bar	           & 0 - 9                  & Continuous \\
    y2bar	           & 0 - 9                  & Continuous \\
    xybar	           & 0 - 9                  & Continuous \\
    x2ybr	           & 0 - 9                  & Continuous \\
    xy2br	           & 0 - 9                  & Continuous \\
    x-ege	           & 0 - 9                  & Continuous \\
    xegvy	           & 0 - 9                  & Continuous \\
    y-ege	           & 0 - 9                  & Continuous \\
    yegvx	           & 0 - 9                  & Continuous
  \end{tabular}
  \item[] \bb{Class Target}: Letter
  \item[] \bb{Class Information}:
  \item[]
  \begin{tabular}{l c c c c }
    \bb{Description} & \bb{Value} & \bb{Count} & \bb{Percentage} \\
    Letter A                & A          & 789        & 0.04\% \\
    Letter B                & B          & 766        & 0.04\% \\
    Letter C                & C          & 736        & 0.04\% \\
    Letter D                & D          & 805        & 0.04\% \\
    Letter E                & E          & 768        & 0.04\% \\
    Letter F                & F          & 775        & 0.04\% \\
    Letter G                & G          & 773        & 0.04\% \\
    Letter H                & H          & 734        & 0.04\% \\
    Letter I                & I          & 755        & 0.04\% \\
    Letter J                & J          & 747        & 0.04\% \\
    Letter K                & K          & 739        & 0.04\% \\
    Letter L                & L          & 761        & 0.04\% \\
    Letter M                & M          & 792        & 0.04\% \\
    Letter N                & N          & 783        & 0.04\% \\
    Letter O                & O          & 753        & 0.04\% \\
    Letter P                & P          & 803        & 0.04\% \\
    Letter Q                & Q          & 783        & 0.04\% \\
    Letter R                & R          & 758        & 0.04\% \\
    Letter S                & S          & 748        & 0.04\% \\
    Letter T                & T          & 796        & 0.04\% \\
    Letter U                & U          & 813        & 0.04\% \\
    Letter V                & V          & 764        & 0.04\% \\
    Letter W                & W          & 752        & 0.04\% \\
    Letter X                & X          & 787        & 0.04\% \\
    Letter Y                & Y          & 786        & 0.04\% \\
    Letter Z                & Z          & 734        & 0.04\%
  \end{tabular}
  \item[] \bb{Missing Attributes}: none
\end{itemize}

@@

\section{Technical Details}
Missing attribute values within the breast cancer dataset were replaced with the mode of the samples of the same class. For the mushroom dataset, as the amount of missing values for attribute 11 was very large, the missing values themselves were simply treated as another category. No discretization occurred as all base algorithms are able to handle continuous data. For all datasets, any sort of identification number or code attributes were removed. Within the E. Coli dataset, the lip and chg categorical attributes were also removed as they provided minimal information. Furthermore, any string values were converted to integers. For example, the ``v-high'', ``high'', ``med'' and ``low'' attribute values would have been converted to 0, 1, 2, 3 respectively.

\subsection{ID3}
\begin{tabular}{ |c|c|c| }
  Dataset            & Max Level & Minimum \# of Samples \\
  Breast Cancer      & None      & SOMETHING            \\
  Car Cancer         & None      & SOMETHING            \\
  Letter Recognition & None      & SOMETHING            \\
  E. Coli            & None      & SOMETHING            \\
  Mushroom           & None      & SOMETHING
\end{tabular}

\subsection{Naïve Bayes}
gaussian

\subsection{AdaBoost on Naïve Bayes}
number of learners

\subsection{AdaBoost on ID3}
number of learners

\subsection{Random Forest}
number of trees

\subsection{K-Nearest Neighbors}
k
distance

@@

\section{Results}
\begin{table}
  \begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    Breast Cancer           & Car      & Letter   & E. Coli  & Mushroom \\ \hline
    AdaBoost on ID3         & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    ID3                     & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    Random Forest           & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    Naïve Bayes             & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    AdaBoost on Naïve Bayes & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    K-Nearest Neighbor      & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
  \end{tabular}
  \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
\end{table}

>>>>

\subsection{Car Data}
\begin{itemize}[leftmargin=*]
  \item[] \bb{Title}: Car Evaluation Database
  \item[] \bb{Date}: June 1997
  \item[] \bb{Number of Samples}: 1728
  \item[] \bb{Number of Attributes}: 6
  \item[] \bb{Attribute Information}:
  \item[]
  \begin{tabular}{l c c c }
    \bb{Description} & \bb{Values}            & \bb{Type} \\
    buying           & v-high, high, med, low & Discrete  \\
    maint            & v-high, high, med, low & Discrete  \\
    doors            & 2, 3, 4, 5-more        & Discrete  \\
    persons          & 2, 4, more             & Discrete  \\
    lug\_boot        & small, med, big        & Discrete  \\
    safety           & low, med, high         & Discrete
  \end{tabular}
  \item[] \bb{Class Target}: Car Quality
  \item[] \bb{Class Information}:
  \item[]
  \begin{tabular}{l c c c c }
    \bb{Description} & \bb{Value} & \bb{Count} & \bb{Percentage} \\
    Unacceptable     & unacc      & 1210       & 70.023\%        \\
    Acceptable       & acc        & 384        & 22.222\%        \\
    Good             & good       & 69         & 3.993\%         \\
    Very Good        & v-good     & 65         & 3.762\%
  \end{tabular}
  \item[] \bb{Missing Attributes}: None
\end{itemize}

\subsection{E. Coli Data}
\begin{itemize}[leftmargin=*]
  \item[] \bb{Title}: Protein Localization Sites
  \item[] \bb{Date}: September 1997
  \item[] \bb{Number of Samples}: 336
  \item[] \bb{Number of Attributes}: 8
  \item[] \bb{Attribute Information}:
  \item[]
  \begin{tabular}{l c c c }
    \bb{Description} & \bb{Values}       & \bb{Type}  \\
    Sequence Name    &  Accession Number & Discrete   \\
    mcg              & 0.00 - 0.89       & Continuous \\
    gvh              & 0.16 - 1.00       & Continuous \\
    lip              & 0.48 - 1.00       & Discrete   \\
    chg              & 0.50 - 1.00       & Discrete   \\
    aac              & 0.00 - 0.88       & Continuous \\
    alm1             & 0.03 - 1.00       & Continuous \\
    alm2             & 0.00 - 0.99       & Continuous
  \end{tabular}
  \item[] \bb{Class Target}:  Localization Site
  \item[] \bb{Class Information}:
  \item[]
  \begin{tabular}{l c c c c }
    \bb{Description}           & \bb{Value} & \bb{Count} & \bb{Percentage} \\
    Cytoplasm                  & cp         & 143        & 42.56\%         \\
    Inner Membrane             & im         & 77         & 22.92\%         \\
    Perisplasm                 & pp         & 52         & 15.48\%         \\
    Inner Membrane Uncleavable & imU        & 35         & 10.42\%         \\
    Outer Membrane             & om         & 20         & 5.95\%          \\
    Outer Membrane             & omL        & 5          & 1.49\%          \\
    Inner Membrane Lipoprotein & imL        & 2          & 0.59\%          \\
    Inner Membrane Cleavable   & imS        & 2          & 0.59\%
  \end{tabular}
  \item[] \bb{Missing Attributes}: None
\end{itemize}

\subsection{Letter Recognition Data}
\begin{itemize}[leftmargin=*]
  \item[] \bb{Title}: Letter Image Recognition Data
  \item[] \bb{Date}: January 1991
  \item[] \bb{Number of Samples}: 20000
  \item[] \bb{Number of Attributes}: 16
  \item[] \bb{Attribute Information}:
  \item[]
  \begin{tabular}{l c c c }
    \bb{Description} & \bb{Values}            & \bb{Type}  \\
    x-box	           & 0 - 9                  & Continuous \\
    y-box	           & 0 - 9                  & Continuous \\
    width	           & 0 - 9                  & Continuous \\
    high 	           & 0 - 9                  & Continuous \\
    onpix	           & 0 - 9                  & Continuous \\
    x-bar	           & 0 - 9                  & Continuous \\
    y-bar	           & 0 - 9                  & Continuous \\
    x2bar	           & 0 - 9                  & Continuous \\
    y2bar	           & 0 - 9                  & Continuous \\
    xybar	           & 0 - 9                  & Continuous \\
    x2ybr	           & 0 - 9                  & Continuous \\
    xy2br	           & 0 - 9                  & Continuous \\
    x-ege	           & 0 - 9                  & Continuous \\
    xegvy	           & 0 - 9                  & Continuous \\
    y-ege	           & 0 - 9                  & Continuous \\
    yegvx	           & 0 - 9                  & Continuous
  \end{tabular}
  \item[] \bb{Class Target}: Letter
  \item[] \bb{Class Information}:
  \item[]
  \begin{tabular}{l c c c c }
    \bb{Description} & \bb{Value} & \bb{Count} & \bb{Percentage} \\
    Letter A                & A          & 789        & 0.04\% \\
    Letter B                & B          & 766        & 0.04\% \\
    Letter C                & C          & 736        & 0.04\% \\
    Letter D                & D          & 805        & 0.04\% \\
    Letter E                & E          & 768        & 0.04\% \\
    Letter F                & F          & 775        & 0.04\% \\
    Letter G                & G          & 773        & 0.04\% \\
    Letter H                & H          & 734        & 0.04\% \\
    Letter I                & I          & 755        & 0.04\% \\
    Letter J                & J          & 747        & 0.04\% \\
    Letter K                & K          & 739        & 0.04\% \\
    Letter L                & L          & 761        & 0.04\% \\
    Letter M                & M          & 792        & 0.04\% \\
    Letter N                & N          & 783        & 0.04\% \\
    Letter O                & O          & 753        & 0.04\% \\
    Letter P                & P          & 803        & 0.04\% \\
    Letter Q                & Q          & 783        & 0.04\% \\
    Letter R                & R          & 758        & 0.04\% \\
    Letter S                & S          & 748        & 0.04\% \\
    Letter T                & T          & 796        & 0.04\% \\
    Letter U                & U          & 813        & 0.04\% \\
    Letter V                & V          & 764        & 0.04\% \\
    Letter W                & W          & 752        & 0.04\% \\
    Letter X                & X          & 787        & 0.04\% \\
    Letter Y                & Y          & 786        & 0.04\% \\
    Letter Z                & Z          & 734        & 0.04\%
  \end{tabular}
  \item[] \bb{Missing Attributes}: None
\end{itemize}

@@

\section{Technical Details}
Missing attribute values within both the breast cancer dataset and mushroom dataset treated as another category. Attempts were initially made to replace the missing values; however, no improvements with accuracy were observed. Furthermore, no discretization occurred as all base algorithms are able to handle continuous data. For each dataset, any sort of identification number or code attributes were removed. Within the E. Coli dataset, the lip and chg categorical attributes were also removed as they provided minimal information. Furthermore, any string values were converted to integers. For example, the ``v-high'', ``high'', ``med'' and ``low'' attribute values would have been converted to 0, 1, 2, 3 respectively.

\subsection{ID3}
\begin{table}
  \caption{The }
  \begin{tabular}{ |c|c| } \hline
    \bb{Dataset}       & \bb{Minimum \# of Samples} \\ \hline
    Breast Cancer      & 1                          \\ \hline
    Car                & 1                          \\ \hline
    E. Coli            & 2                          \\ \hline
    Letter Recognition & 1                          \\ \hline
    Mushroom           & 1                          \\ \hline
  \end{tabular}
\end{table}

\subsection{Naïve Bayes}
\begin{tabular}{ |c|c| } \hline
  \bb{Dataset}       & \bb{Distribution} \\ \hline
  Breast Cancer      & None              \\ \hline
  Car                & None              \\ \hline
  E. Coli            & Gaussian          \\ \hline
  Letter Recognition & Gaussian          \\ \hline
  Mushroom           & None              \\ \hline
\end{tabular}

\subsection{AdaBoost on ID3}
\begin{tabular}{ |c|c|c| } \hline
  \bb{Dataset}       & \bb{Max Level} & \bb{\# of Learners} & Proportion of Samples \\ \hline
  Breast Cancer      & 1              & 100                 & 0.50                  \\ \hline
  Car                & 1              & 100                 & 0.70                  \\ \hline
  E. Coli            & 1              & 100                 & 0.50                   \\ \hline
  Letter Recognition & 1              & IDK                 & IDK                   \\ \hline
  Mushroom           & 1              & 10                  & 0.30                   \\ \hline
\end{tabular}

\subsection{AdaBoost on Naïve Bayes}
\begin{tabular}{ |c|c|c| } \hline
  \bb{Dataset}       & \bb{Distribution} & \bb{\# of Learners} & Proportion of Samples & \\ \hline
  Breast Cancer      & None              & 100                 & 0.70                    \\ \hline
  Car                & None              & 100                 & 0.40                    \\ \hline
  E. Coli            & Gaussian          & 150                 & 0.30                     \\ \hline
  Letter Recognition & Gaussian          & IDK                 & IDK                     \\ \hline
  Mushroom           & None              & 10                  & 0.30                     \\ \hline
\end{tabular}

\subsection{Random Forest}
\begin{tabular}{ |c|c| } \hline
  \bb{Dataset}       & \bb{\# of Learners} & Proportion of Samples \\ \hline
  Breast Cancer      & 120                 & 0.70                  \\ \hline
  Car                & 200                 & 0.60                  \\ \hline
  E. Coli            & 120                 & 0.70                  \\ \hline
  Letter Recognition & 50                  & 0.30                  \\ \hline
  Mushroom           & 10                  & 0.30                  \\ \hline
\end{tabular}

\subsection{K-Nearest Neighbors}
\begin{tabular}{ |c|c| } \hline
  \bb{Dataset}       & \bb{K}    & Distance \\ \hline
  Breast Cancer      & 1                   & Hamming \\ \hline
  Car                & 1                   & Hamming \\ \hline
  E. Coli            & 1                   & Euclidian \\ \hline
  Letter Recognition & 1                   & Euclidian \\ \hline
  Mushroom           & 1                   & Hamming \\ \hline
\end{tabular}

@@

\section{Results}
\begin{table}
  \begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    Algorithm               Breast Cancer   & Car      & Letter   & E. Coli  & Mushroom \\ \hline
    ID3                     & 97.994\%      & 90.634\% & 81.909\% & 100.00\% & 99.998\% \\ \hline
    Naïve Bayes             & 97.663\%      & 81.940\% & 79.455\% & 100.00\% & 95.952\% \\ \hline
    AdaBoost on ID3         & 98.715\%      & 88.822\% & 83.389\% & 100.00\% & 97.590\% \\ \hline
    AdaBoost on Naïve Bayes & 98.626\%      & 91.367\% & 77.725\% & 100.00\% & 100.00\% \\ \hline
    Random Forest           & 97.592\%      & 91.175\% & 84.316\% & 100.00\% & 100.00\% \\ \hline
    K-Nearest Neighbor      & 98.050\%      & 89.763\% & 87.886\% & 100.00\% & 100.00\% \\ \hline
  \end{tabular}
  \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
\end{table}

\begin{table}
  \begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    Algorithm               & Breast Cancer & Car      & Letter   & E. Coli  & Mushroom \\ \hline
    ID3                     & 1.465\%       & 4.061\%  & 8.981\%  & 100.00\% & 0.017\% \\ \hline
    Naïve Bayes             & 1.678\%       & 3.373\%  & 10.388\% & 100.00\% & 2.128\% \\ \hline
    AdaBoost on ID3         & 1.216\%       & 3.085\%  & 6.678\%  & 100.00\% & 2.038\% \\ \hline
    AdaBoost on Naïve Bayes & 1.394\%       & 1.987\%  & 9.275\%  & 100.00\% & 100.00\% \\ \hline
    Random Forest           & 1.597\%       & 5.171\%  & 9.711\%  & 100.00\% & 100.00\% \\ \hline
    K-Nearest Neighbor      & 1.118\%       & 3.967\%  & 7.001\%  & 100.00\% & 100.00\% \\ \hline
  \end{tabular}
  \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
\end{table}
